Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-15 paper/main.tex
Removed old optimized results
QA till Discussion. Added \text in math environ

\usepackage[numbers]{natbib} % We need to tweak our referencing a bit.
\usepackage{appendix} % Fixes formatting of appendices
\usepackage[printonlyused]{acronym} % Package to handle the acronym list
\usepackage{graphicx} % We *may* use images
\graphicspath{{images/}} % and it is clean to put them in a separate dir
\usepackage{hyperref} % Internal and external links is nice
\hypersetup{pdfborder=0 0 0} % ..especially without red borders

@@

\section{SUPERCOP benchmarks}
The results of the \ac{SHA}-3 256-bit functions and \ac{SHA}-256 benchmarking in
\ac{SUPERCOP} can be found in \autoref{app:supercop:bench}.

\subsection{Double SHA-256 Estimates}
\ac{SUPERCOP} does not measure the speed of double \ac{SHA}-256, so we have no exact
value of how many cycles this should take, we can however estimate it. For every hash
calculation double \ac{SHA}-256 will have to hash an extra 32-byte.
\ac{SUPERCOP} does not give results for hashing 32-byte, so this will also have
to be estimated. The calculations of worst-case scenario (cycles/byte for 32
byte is the same as 8 byte), best-case (cycles/byte for 32 byte is the same as
for 64 byte) and interpolation (assuming linear decrease) are shown in Table
\ref{tbl:supercop:sha256d}. The calculation for this table are as follows:

$$\frac{median * size + 179.62*32}{size} = SHA256d\ estimate (worst-case)$$

$$\frac{median * size + 38.12*32}{size} = SHA256d\ estimate (best-case)$$

$$179.62 + \frac{38.12-179.62}{64-8}*(32-8) = 118.97 (cycles/byte for 32 byte)$$

$$\frac{median * size + 118.97*32}{size} = SHA256d\ estimate (interpolation)$$

@@

Interpolation gives a somewhat pessimistic result of the cycles/byte needed for
hashing 32 byte, so the probable speed is somewhere in between the
interpolation point and the best case time.

@@

\section{Measurements of Tahoe operations Using Test Vectors}
The sum of the amount of time it took for the underlying hash library to
calculate the hash operations are exhibited in Figures \ref{fig:graph:1001b},
\ref{fig:graph:1001kb}, \ref{fig:graph:501mb}, \ref{fig:graph:5100mb} and
\ref{fig:graph:11gb}. We call this \emph{Time spent hashing}.

@@

\section{Eliminating overhead in measurements}
The following measurements were done to eliminate the overhead introducer by
our work.

\paragraph{Cython bindings}
To eliminate as much as possible of overhead introduced by our bindings, we
timed the calls from our bindings to the underlying C-function. The overhead
should be the same for all bindings, since the Cython code is the same. The
measured overhead, calculated from BLAKE can be seen in Table
\ref{tbl:cython:overhead}.

@@

\paragraph{Modification to Tahoe-\ac{LAFS}}
Because we write to two files after each hash calculation, this will create an
overhead in the measurements that would not normaly exist in Tahoe-\ac{LAFS}.
This overhead should be about the same for all candidates, since the number of
writes are equal. The results and calculations for this overhead, based on runs
with double \ac{SHA}-256 can be seen in Table \ref{tbl:measure:overhead}.

@@

\subsection{Optimizing results}
We have not used the fastest possible implementations possible for various
reasons mentioned previously. However, if we had actually used the fastest
implementations in \ac{SUPERCOP}, achieved median speed for every hash

>>>>

\usepackage[numbers]{natbib} % We need to tweak our referencing a bit.
\usepackage{appendix} % Fixes formatting of appendices
\usepackage[printonlyused]{acronym} % Package to handle the acronym list
\usepackage{graphicx} % We *may* use images
\graphicspath{{images/}} % and it is clean to put them in a separate dir
\usepackage{hyperref} % Internal and external links is nice
\hypersetup{pdfborder=0 0 0} % ..especially without red borders
\usepackage{amstext} % To support \text in math mode

@@

\section{SUPERCOP benchmarks}

The results of the \ac{SHA}-3 256-bit functions and \ac{SHA}-256 benchmarking in
\ac{SUPERCOP} can be found in \autoref{app:supercop:bench}.

BLAKE, \ac{BMW}, and Luffa outperform \ac{SHA}-256 on cycles per
byte for all tests. For larger input sizes, Simd and Luffa also do the
calculations quicker than \ac{SHA}-256.

\subsection{Double SHA-256 Estimates}

\ac{SUPERCOP} does not measure the speed of double \ac{SHA}-256, so we have no exact
value of how many cycles this should take, we can however estimate it. For every hash
calculation double \ac{SHA}-256 will have to hash an extra 32-byte.
\ac{SUPERCOP} does not give results for hashing 32-byte, so this will also have
to be estimated. The calculations of worst-case scenario (cycles/byte for 32
byte is the same as 8 byte), best-case (cycles/byte for 32 byte is the same as
for 64 byte) and interpolation (assuming linear decrease) are shown in Table
\ref{tbl:supercop:sha256d}. The calculation for this table are as follows:

$$\frac{median * size + 179.62*32}{size} = \text{SHA256d estimate (worst case)}$$

$$\frac{median * size + 38.12*32}{size} = \text{SHA256d estimate (best case)}$$

$$179.62 + \frac{38.12-179.62}{64-8}*(32-8) = 118.97 \text{(cycles/byte for 32 byte)}$$

$$\frac{median * size + 118.97*32}{size} = \text{SHA256d estimate (interpolation)}$$

@@

Interpolation gives a somewhat pessimistic result of the cycles/byte needed for
producing the digest of 32 bytes, so the probable speed is somewhere in between the
interpolation point and the best-case time.

@@

\section{Measurements of Tahoe operations Using Test Vectors}

The sum of the amount of time it took for the underlying hash libraries to
produce the digests are exhibited in Figures \ref{fig:graph:1001b},
\ref{fig:graph:1001kb}, \ref{fig:graph:501mb}, \ref{fig:graph:5100mb} and
\ref{fig:graph:11gb}. We call this \emph{Time spent hashing}.

@@

\section{Eliminating overhead in measurements}

The following measurements were done to eliminate the overhead introduced by
our work.

\paragraph{Cython bindings.}
To eliminate as much as possible of overhead introduced by our bindings, we
timed the calls from our bindings to the underlying C-function. The overhead
should be the same for all bindings, since the Cython code is the same. The
measured overhead, calculated from BLAKE can be seen in Table
\ref{tbl:cython:overhead}.

@@

\paragraph{Modification to Tahoe-\ac{LAFS}.}
Because we write to two files after each call to {\verb digest }, an overhead in
the measurements that would not normally exist in Tahoe-\ac{LAFS}, will be
created. This overhead should be about the same for all candidates, since the
number of writes are equal. The results and calculations for this overhead,
based on runs with double \ac{SHA}-256, can be seen in Table
\ref{tbl:measure:overhead}.

@@
